Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-06 paper/sec-analysis.tex
work on paper

We now justify some of the cuts that we are using.
%
As mentioned before, the cuts in each category are separately
optimised in an inclusive analysis: it is only we have determined
which is the dominant category that the analysis is made exclusive.
%
We begin with the boosted category.
%
In Fig.~\ref{fig:cutplots1} we show
the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/pt_H0_res_C1_boost.pdf}
\caption{\small Left plot: the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
}
\label{fig:cutplots1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We now justify some of the cuts that we are using.
%
As mentioned before, the cuts in each category are separately
optimised in an inclusive analysis: it is only we have determined
which is the dominant category that the analysis is made exclusive.
%
We begin with the boosted category.
%
In Fig.~\ref{fig:cutplots1} we show
the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
  %
  We see that the background distribution
  falls off rather steeply than the signal, therefore
  suggesting that the boosted region should be
  advantageous to suppress the background.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/pt_H0_res_C1_boost.pdf}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1_boost.pdf}
\caption{\small Left plot: the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
  %
  Right plot: the invariant mass of the leading Higgs
  candidate.
}
\label{fig:cutplots1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

In Fig.~\ref{fig:cutplots1} we also show the distribution
of the invariant mass of the leading Higgs candidates.
%
The signal is of course well peaked at $m_h=125$ GeV, the physical
mass, while the background does not display any structure.
%
Note that the smearing, which mimics detector resolution effects,
leads to a rather broad distribution which reduces the usefulness
of the Higgs mass window cut.
%
However, the information of the different shape of the $m_{h}$
distribution will still be exploited by the MVA.

As explained above, in the boosted category we also require the two
leasing subjets of the large-$R$ jet to be relatively
hard.
%
In Fig ...

### 2015-07-06 paper/sec-conclusions.tex
more work on text
work on paper

\section{Conclusions and outlook}

In this work we have presented a detailed study of the feasibility
of the measurement of Higgs pair production in the $bb\bar{b}\bar{b}$
final state at the High-Luminosity LHC....

@@

{\bf\noindent  Acknowledgments \\}
We thank A.~Papaefstathiou for useful discussions on this project.
%
J.~R. is supported by an STFC Rutherford Fellowship ST/K005227/1.
%
J.~R. and N.~H. are
supported by an European Research Council Starting Grant "PDF4BSM".
%

>>>>

\section{Conclusions and outlook}
\label{sec:conclusions}

In this work we have presented a detailed study of the feasibility
of the measurement of Higgs pair production in the $bb\bar{b}\bar{b}$
final state at the High-Luminosity LHC.
%
As opposed to previous works, we have combined a traditional
cut-based analysis with a modern multivariate analysis,
which allows one to significantly improve the signal significance.
%
A careful analysis of the different possible methods to reconstruct
Higgs pairs finds that the boosted category is the most efficient
one, but that additional complementary information can also be provided
by the intermediate and resolved categories.
%
Our analysis includes all relevant backgrounds, including the
effects from fake $b$-tags, neglected in previous works,
which turn out to be quite important specially
in the boosted and in the resolved categories.

Thanks for the MVA improvements, and combining the information
from the three exclusive categories, we find a signal significance
of 3.8.
%
Therefore, we can conclude that, already on the $4b$ channel along,
it should be possible to observe evidence for this process at
the HL-LHC.
%
A combination with other decay channels, like $b\bar{b}\gamma\gamma$
and $b\bar{b}\tau\tau$ would still be required in order
to claim discovery of Higgs pair production.

One important implication of our results is which is the accuracy
that can be achieved for a measurement of the
Higgs trilinear coupling $\lambda$ from a measurement
of the $4b$ final state.
%
We plan to quantify this in future work.
%
In addition,
in this work we have considered only SM production mechanism,
but it is well known that many BSM scenarios predict deviations
in Higgs pair production, both at the level of rates,
for instance when the trilinear coupling $\lambda$, and of
shapes of the distributions, when higher-order effective
operators are included in the theory~\cite{Azatov:2015oxa}.
%
In this respect, we plan to study which are the constraints
on BSM physics that can be obtained from measurements
of Higgs pair production in the $4b$ channel.
%
This however will be a computationally intensive task since in
general BSM physics modify the shapes of the Higgs kinematical
distributions, and thus each different point in the parameter
space would require a re-optimization via a new training
of the MVA.

@@

{\bf\noindent  Acknowledgments \\}
We thank R.~Contino, A.~Papaefstathiou and
G.~Salam for useful discussions on the topic
of Higgs pair production.
%
J.~R. is supported by an STFC Rutherford Fellowship ST/K005227/1.
%
J.~R. and N.~H. are
supported by an European Research Council Starting Grant "PDF4BSM".
%
N.~B.~N. is supported by a PhD scholarship from the Malaysia
government.
K.~B. is supported by a studentships from the Rhodes Foundation.
%
J.~F. and C.~I. are supported by the STFC.

### 2015-07-06 paper/sec-mcsamples.tex
work on paper

>>>>

\subsection{Smearing}

It is beyong the scope of this work to perform a complete study of the impact of
detector effects in this process.
%
However, it is still important to include some form of rough estimate of detector
effects in the analysis.
%
In this work we simulate the finite momentum resolution of the ATLAS and CMS
hadronic calorimenters by ....

### 2015-07-06 paper/sec-mva.tex
work on paper

The classification of events as arising from either signal or
background processess via the use of a multivariate analysis is a common
technique in high energy physics.

@@

\begin{itemize}
\item The $k_T$ splitting scale of the fat-jet (Reference).
\item The ratio of 2-to-1-Subjettiness $\tau_{2}/\tau_{1}$ of the fat-jet (Reference).
\item The fat-jet energy correlation function double-ratio $C_2$ (Reference).
\item The fat-jet energy correlation function double-ratio $D_2$ (Reference).
\end{itemize}

@@

Given the above set of kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ as the probability that the event $i$ originates from the signal process,
\be y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} ), \ee
where $y_i^\prime$ represents the true classification of the event $i$, i.e $y^\prime_{\text{signal}} = 1$ and $y^\prime_{\text{background}} = 0$. With this interpretation, our general classification probability including background events is given by
\be
P(y_i^\prime|\{k\}_i, \{\omega\}) = y_i^{y^\prime_i}(1-y_i)^{1-y^\prime_i}.
\ee
 Correspondingly the negative log-liklihood cost function to be used in the neural network training is the cross-entropy error
\be E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right) = \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)}. \ee

Using the cross-entropy cost function, the neural networks are trained with a basic genetic algorithm (GA) over 50,000 generations.
(Do we need to specifiy GA params etc?).
\subsection{Enhancing signal discrimination with the MVA}

@@

>>>>

The classification of events as arising from either signal or
background processes via the use of a multivariate analysis is a common
technique in high energy physics.

@@

\begin{itemize}
\item The $k_T$ splitting scale of the fat-jet (Reference).
\item The ratio of 2-to-1-Subjetiness $\tau_{2}/\tau_{1}$ of the fat-jet (Reference).
\item The fat-jet energy correlation function double-ratio $C_2$ (Reference).
\item The fat-jet energy correlation function double-ratio $D_2$ (Reference).
\end{itemize}

@@

Given the above set of kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ as the probability that the event $i$ originates from the signal process,
\be y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} ), \ee
where $y_i^\prime$ represents the true classification of the event $i$, i.e $y^\prime_{\text{signal}} = 1$ and $y^\prime_{\text{background}} = 0$. With this interpretation, our general classification probability including background events is given by
\be
P(y_i^\prime|\{k\}_i, \{\omega\}) = y_i^{y^\prime_i}(1-y_i)^{1-y^\prime_i}.
\ee
 Correspondingly the negative log-likelihood cost function to be used in the neural network training is the cross-entropy error
\be E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right) = \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)}. \ee

Using the cross-entropy cost function, the neural networks are trained with a basic genetic algorithm (GA) over 50,000 generations.
(Do we need to specify GA params etc?).
\subsection{Enhancing signal discrimination with the MVA}

@@

\subsection{Another look at jet substructure variables}

It is now worth trying to understand where does the increase in signal significance
achieved after the MVA comes from.
%
As we will show now, the MVA has correctly identified which of the substructure
variables are more discriminant between signal and background distributions,
and combined this information to determine an optimal cut to maximize signal
significance.

For instance, in the boosted category, the analyses of the
size of the neural network weights clearly indicates that the subjetiness
$\tau_{12}$ and the energy correlations $C_2$ are two of the most useful
variables.
%
To verify that indeed these two variables are quite different between signal
and background events, in Fig.~\ref{fig:mva_substructure_1}
we show the subjetiness $\tau_{12}$ and the energy correlation between
signal and background.
%
We indeed verify that the two shapes are quite different,
reflecting the differences in the internal structure of jets
between QCD jets and jets originated from the Higgs decays.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/tau21_H0_res_C1_boost.pdf}
  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_H0_res_C1_boost.pdf}
  \caption{\small Left plot: subjetiness.
    Right plot: energy correlations.
}
\label{fig:mva_substructure_1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-06 paper/sec-optimisation.tex
work on paper

%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
    Scenario  &  $f_b$  &  $f_l$  &  $\Delta p_T$ \\
    \hline
    \hline
    Baseline  &  0.8   &   0.01  &  5\% \\
    \hline
    A        &  0.9   &   0.01  &  5\% \\
    B        &  0.7   &   0.01  &  5\% \\
    C        &  0.8   &   0.005  &  5\% \\
    D        &  0.8   &   0.02  &  5\% \\
    E        &  0.9   &   0.005  &  2\% \\   
    \hline
  \end{tabular}
  \caption{\small The baseline settings for the $b$-jet
    tagging probability, the light jet mistag rate $f_l$
    and the $p_T$ resolution $\Delta p_T$, compared
    to the various scenarios that we discusse in this section.
\label{sec:variations}
  }
  \end{table}
%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
    Scenario  &  $f_b$  &  $f_l$  &  $\Delta p_T$ \\
    \hline
    \hline
    Baseline  &  0.8   &   0.01  &  5\% \\
    \hline
    A        &  0.9   &   0.01  &  5\% \\
    B        &  0.7   &   0.01  &  5\% \\
    C        &  0.8   &   0.005  &  5\% \\
    D        &  0.8   &   0.02  &  5\% \\
    E        &  0.9   &   0.005  &  2\% \\   
    \hline
  \end{tabular}
  \caption{\small The baseline settings for the $b$-jet
    tagging probability, the light jet mistag rate $f_l$
    and the $p_T$ resolution $\Delta p_T$, compared
    to the various scenarios that we discussed in this section.
\label{sec:variations}
  }
  \end{table}
%%%%%%%%%%%%%%%%%%%

We also study how the signal significance is modified as a function
of the systematic uncertainty that needs to be obtained
in the measurement of the background processes.
%
This is specially important in a process like this one where
the signal over background ratio $S/B$ is small, and thus were
it is essential to measure the backgrounds as accurately
as possible.

### 2015-07-06 paper/sec-results.tex
work on paper

We consider the following levels of the cut-flow
\begin{itemize}
\item {\bf C0}: these are the cross-sections at the generator
  level, before any analysis cuts
\item {\bf C1}: results after the basic jet selection
  and related cuts, but before $b$-tagging.
\item {\bf C2}: results after the $b$-tagging, but
  before applying the invariant mass window cut
\item {\bf C3}: final results of the cut-based
  analysis
  \end{itemize}
We consider the results for the individual categories, using the
exclusive priorisation discussed in the previous section.
%
In Appendix.~\ref{sec:overlap} we comment
interplay of the overlap between the various categories.
%
At each stage of the cut flow, we also provide the number
of events that would be expected at the HL-LHC with
an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
the signal significance $S/\sqrt{B}$ and the signal
over background ratio $S/B$.
%
Results are shown both for the signal and for all backgrounds
combined.
%
The results for the three categories have been collected in
Table~\ref{table:cutflowboosted}.

We emphasize that it is important not only to achieve a good signal
significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a measurement of the background with an unfeasibly small
systematic uncertainty would be required.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c||c|c||c|c}
    \hline
    \multicolumn{7}{c}{Boosted category}\\
    \hline
    \hline
    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
        {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &  0.46    & $1.3\,10^6$    &  $1.4\,10^3$   & $3.9\,10^9$     & 0.022     &  $3.5\,10^{-7}$ \\
        {\bf C2}  &  0.064     &  12.6     &  193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Intermediate category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
         {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &   1.44    &   $1.1\,10^{7}$  &  $4.3\,10^3$   &  $3.3\,10^{10}$    &  0.024    &  $1.3\,10^{-7}$ \\
        {\bf C2}  &   0.22    &  722   &  660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Resolved category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
       {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &   3.34    & $7.5\,10^{7}$    & $1.1\,10^4$    & $3.3\,10^{10}$     & 0.021     & $4.5\,10^{-8}$  \\
        {\bf C2}  &   0.54    &  $3.5\,10^{3}$   &  $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$ \\
        \hline
  \end{tabular}
  \caption{\small Cut-flow for the analysis of the boosted (top),
    intermediate (middle) and resolved (bottom)
    categories.
    %
    At each level of the cut-flow, we indicate the cross-sections and the number of
    expected events at the HL-LHC for $\mathcal{L}_{\rm int}=3$ ab$^{-1}$, both for
    signal events and for all the backgrounds combined.
    %
    We also provide in each case the
    signal significance $S/\sqrt{B}$ and the signal
    over background ratio $S/B$.
    %
    The first row {\bf C0} is the generator-level result and thus is common
    to all three categories.
    %
    See text for more details.
    \label{table:cutflowboosted}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Both the intermediate and resolved categories benefit from higher signal yields,
specially in the resolved category, but this enhancement is cancellend by the stronger
increase in the QCD multijet background.
%
We see that in both cases the signal significance is around half of that in the boosted category,
with in addition $S/B$ being an order of magnitude smaller.
%
Therefore, the boosted category is clearly determined to be the most useful category,
specially due to the significant suppression of the QCD multijet background.
%
And we still have not exploited all the rich information contained on the jet
substructure, as we will do in the next section.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c||c|c||c|c}
    \hline
    \multicolumn{7}{c}{Boosted category}\\
    \hline
    \hline
    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
        {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
        {\bf C1}  &  0.46    & $1.0\,10^2$    &  $1.4\,10^3$   & $3.1\,10^5$     & 2.48     &  $4.4\,10^{-3}$ \\
        {\bf C2}  &  0.064     &  7.1     &  193   &  $2.1\,10^4$    &  1.30    &  $9.1\,10^{-3}$ \\
        \hline
  \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflowboosted}, but now
    only with the QCD $4b$ multi-jet background taken into account.
    %
    \label{table:cutflowboosted4B}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We consider the following levels of the cut-flow
\begin{itemize}
\item {\bf C0}: these are the cross-sections at the generator
  level, before any analysis cuts
\item {\bf C1}: results after the basic jet selection
  and related cuts, but before $b$-tagging.
\item {\bf C2}: results after the $b$-tagging, but
  before applying the invariant mass window cut
\item {\bf C3}: final results of the cut-based
  analysis
  \end{itemize}
We consider the results for the individual categories, using the
exclusive priorisation discussed in the previous section.
%
In Appendix.~\ref{sec:overlap} we comment
interplay of the overlap between the various categories.
%
At each stage of the cut flow, we also provide the number
of events that would be expected at the HL-LHC with
an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
the signal significance $S/\sqrt{B}$ and the signal
over background ratio $S/B$.
%
Results are shown both for the signal and for all backgrounds
combined.
%
The results for the three categories have been collected in
Table~\ref{table:cutflow}.

We emphasize that it is important not only to achieve a good signal
significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a measurement of the background with an infeasible small
systematic uncertainty would be required.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c||c|c||c|c}
    \hline
    \multicolumn{7}{c}{Boosted category}\\
    \hline
    \hline
    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
        {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &  0.46    & $1.3\,10^6$    &  $1.4\,10^3$   & $3.9\,10^9$     & 0.022     &  $3.5\,10^{-7}$ \\
        {\bf C2}  &  0.064     &  12.6     &  193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Intermediate category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
         {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &   1.44    &   $1.1\,10^{7}$  &  $4.3\,10^3$   &  $3.3\,10^{10}$    &  0.024    &  $1.3\,10^{-7}$ \\
        {\bf C2}  &   0.22    &  722   &  660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Resolved category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
       {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
        {\bf C1}  &   3.34    & $7.5\,10^{7}$    & $1.1\,10^4$    & $3.3\,10^{10}$     & 0.021     & $4.5\,10^{-8}$  \\
        {\bf C2}  &   0.54    &  $3.5\,10^{3}$   &  $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$ \\
        \hline
  \end{tabular}
  \caption{\small Cut-flow for the analysis of the boosted (top),
    intermediate (middle) and resolved (bottom)
    categories.
    %
    At each level of the cut-flow, we indicate the cross-sections and the number of
    expected events at the HL-LHC for $\mathcal{L}_{\rm int}=3$ ab$^{-1}$, both for
    signal events and for all the backgrounds combined.
    %
    We also provide in each case the
    signal significance $S/\sqrt{B}$ and the signal
    over background ratio $S/B$.
    %
    The first row {\bf C0} is the generator-level result and thus is common
    to all three categories.
    %
    See text for more details.
    \label{table:cutflow}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Both the intermediate and resolved categories benefit from higher signal yields,
specially in the resolved category, but this enhancement is canceled by the stronger
increase in the QCD multi-jet background.
%
We see that in both cases the signal significance is around half of that in the boosted category,
with in addition $S/B$ being an order of magnitude smaller.
%
Therefore, the boosted category is clearly determined to be the most useful category,
specially due to the significant suppression of the QCD multi-jet background.
%
And we still have not exploited all the rich information contained on the jet
substructure, as we will do in the next section.

@@

Concerning the other categories, we see that that ignoring the fakes can lead to a substantial
distortion of the results.
%
In the intermediate category, the signal significance is now much better, with $S/sqrt{B}$ increasing from
0.5 with all the backgrounds to $1.57$ if only $4b$ are accounted for, a factor 3 improvement.
%
Also the resolved category improves substantially, with signal significance increasing by a factor 2.
%
Therefore, we conclude that a careful modeling of the fakes is very important to truly quantify
the feasibility of Higgs pair production in the $4b$ channel, though for the most
important category, the boosted category, the results are relatively stable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c||c|c||c|c}
    \hline
    \multicolumn{7}{c}{Boosted category}\\
    \hline
    \hline
    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
        {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
        {\bf C1}  &  0.46    & $1.0\,10^2$    &  $1.4\,10^3$   & $3.1\,10^5$     & 2.48     &  $4.4\,10^{-3}$ \\
        {\bf C2}  &  0.064     &  7.1     &  193   &  $2.1\,10^4$    &  1.30    &  $9.1\,10^{-3}$ \\
        \hline
  \end{tabular}
   $\,$\\
  \vspace{0.4cm}
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Intermediate category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
 {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
        {\bf C1}  &  0.46    & $7.2\,10^2$    &  $1.4\,10^3$   & $2.2\,10^6$     & 2.91     &  $1.9\,10^{-3}$ \\
        {\bf C2}  &  0.064     &  58.8     &  193   &  $1.8\,10^5$    &  1.57    &  $3.7\,10^{-3}$ \\
        \hline
  \end{tabular}
  $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c|c|c|c}
    \hline
    \multicolumn{7}{c}{Resolved category}\\
    \hline
    \hline
    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
    &   $S/\sqrt{B}$  & $S/B$\\
      &    Signal & Back   &  Signal  & Back
    &   & \\
    \hline
 {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
        {\bf C1}  &  0.46    & $9.0\,10^3$    &  $1.4\,10^3$   & $2.7\,10^7$     & 1.92     &  $3.7\,10^{-4}$ \\
        {\bf C2}  &  0.064     &  986     &  193   &  $2.9\,10^6$    &  0.95  &  $5.5\,10^{-4}$ \\
        \hline
  \end{tabular}
  \caption{\small Same as Table~\ref{table:cutflow}, but now
    only with the QCD $4b$ multi-jet background taken into account.
    %
    \label{table:cutflow4B}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
